---
title: "BayesPen: Bayesian Penalized Credible Regions"
output:
  html_document:
    theme: flatly
    highlight: tango
---

## Overview
The **BayesPen** package implements variable and confounder selection via penalized credible regrions. The methods are detailed in the following papers

Bondell HD, Reich BJ. 2012. Consistent high-dimensional Bayesian variable selection via penalized credible regions. *J. Am. Stat. Assoc.* 107: 1610–1624.

Wilson A, Reich BJ. 2014. Confounder selection via penalized credible regions. *Biometrics* 70: 852–861.

The citation for this package is 

Ander Wilson, Howard D. Bondell and Brian J. Reich (2015). BayesPen: Bayesian Penalized Credible Regions. R package version 1.2.

## Installation

The **BayesPen** package can be installed using devtools.
```
library(devtools)
install_github(repo="BayesPen", username="AnderWilson")
library(BayesPen)
```

## An Example
First load the R package.
```{r}
library(BayesPen)
```


### Variable Selection via Penalized Credible Regions
Simulate data.
```{r}
set.seed(1234)
dat <- SimExample(500,model="BR1")
X <- dat$X
y <- dat$y
```

Fit the full model assuming flat priors on beta
```{r}
fit1 <- lm(y~X-1)
betahat <- coef(fit1)
cov <- vcov(fit1)
```

Find solution path
```{r}
fit.BayesPen <- BayesPen(beta=betahat, beta_cov=cov)
```

Refit the model.
```{r}
refit <- BayesPen.refit(y,X,fit.BayesPen)
```

Plot the solution path.
```{r}
BayesPen.plot(refit)
```


### Confounder Selection via Penalized Credible Regions
```{r}
set.seed(1234)
dat <- SimExample(500,model="WPD2")
X <- dat$X
U <- dat$U
W <- cbind(X,U)
y <- dat$y
```

Fit the full outcome model assuming flat priors on beta.
```{r}
fit1 <- lm(y~W-1)
betahat <- coef(fit1)
cov <- vcov(fit1)
```

Fit the full exposure model assuming flat priors on beta.
```{r}
fit2 <- lm(X~U-1)
gammahat <- coef(fit2)
```

Find solution path.
```{r}
fit.BayesPen <- BayesPen(beta=betahat, beta_cov=cov, confounder.weights=c(0,gammahat), force=1)
```

Refit the outcome model.
```{r}
refit <- BayesPen.refit(y,W,fit.BayesPen)
```

Plot the solution path.
```{r}
BayesPen.plot(refit)
```